Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
refactoring proof

  \vspace{.4em}
  \textbf{Case} ($t = \$x$)
  \vspace{.4em}

    The case for $t = \$x$ follows a similar line of reasoning. We start by evaluating the right-hand side:

@@

    Expanding further, this becomes:

@@

    As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:

        \[
    \begin{array}{llll}
      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
            & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(pfx,PG^A,\Pref^A)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

\vspace{5em}
\todo{---------------- OLD STUFF -------------------}
\begin{thm}
  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:

  $$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f),G)$$

  \begin{proof} \text{ }

    Suppose that $pol = p_1, \dots, p_n$. Each $p_i$ has the form $(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik})$. Then by evaulating:

    \[ \begin{array}{lcl}
      con(pol,\Gamma,f) & = & con(p_1,\dots,p_n,\Gamma,f) \\
                        & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
                        & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k},\Gamma,f), \\
                        &   & \dots, \\
                        &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk},\Gamma,f) \\
    \end{array} \]

    For each test $t_i$, if $t_i = pfx$, then we get

    \[ \begin{array}{ll}
          & con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) \\
        = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \\
    \end{array} \]

    For each test $t_i$, if $t_i = \$x$, then we get

    \[ \begin{array}{lcl}
        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) 
            & = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{i1}), \\
            &   & \dots, \\ 
            &   & {pfx}_{ij} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{ij}), \\
            &   & \\
            &   & \text{for each } (pfx_{ij}, l_{ij}) \in \Gamma(x) \\
    \end{array} \]

    Next we compute $compile(con(pol,\Gamma,f), G)$:

    \[ \begin{array}{ll}
        & compile(con(pol,\Gamma,f), G)  \\
                          & \\
                         =& compile_{mBGP}( \\
                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk},G ) \\
                          &  ) \\
    \end{array} \]

    \vspace{.5em}
    This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.

    \vspace{1em}
    Similarly, we can compute $compile(pol, G^A)$:

    \[ \begin{array}{ll}
        & compile(pol,G^A)  \\
                      & \\
                     =& compile_{mBGP}( \\
                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
                      & ~~~~ \dots, \\
                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik}, G^A ), \\
                      & ) \\
    \end{array} \]

    This results in a series of prefixes, product graphs, and orderings of the form $(t_i, PG^A_i, ord^A_i)$.

    We know the follwing:

    \begin{itemize}
      \item each $PG^A_i$ and $PG_{ij}$ are related by $f_{pg}$
      \vspace{-.2em}
      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
    \end{itemize}

  \[ \begin{array}{l}
     con(\textbf{compile}_\textbf{mBGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
  \end{array} \]%

Unfold definition of $\text{compile}_\text{mBGP}$

  \[ \begin{array}{l}
     ~~~~~ con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
  \end{array} \]%

  Apply the definition of $con$

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

  Rewrite $con$ on $rc$

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = con(\mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  \vspace{1em}
  \textbf{Case 1}: Assume $t_i = pfx_{i1}$. Look at:

  \[ \begin{array}{l}
     ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  Rewrite on $in$ and $out$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  Rewrite $con$ on $in$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs given by the previous lemma

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  Since $ord^A_i(f_{pg}(m)) = ord_{i1}(m)$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  Since product graphs have equivalent states

>>>>

  \vspace{.4em}
  \noindent
  \textbf{Case} ($t = \$x$)
  \vspace{.4em}

    \noindent
    The case for $t = \$x$ follows a similar line of reasoning. We start by evaluating the right-hand side:

@@

    \noindent
    Expanding further, this becomes:

@@

    \noindent
    As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:

        \[
    \begin{array}{llll}
      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
            & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(\$x,PG^A,\Pref^A)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

  \noindent
  Note that $PG_i$ and $PG^A$, as well as $\Pref$ and $\Pref^A$ are related by the lemmas from the previous section. Next we further expand on the left side for the abstract topology to show it is equivalent:

  \[ \begin{array}{l}
     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ \$x \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~], \Gamma, f, G) \\
  \end{array} \]%

  Apply the definition of $\Con$:

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow \Con(rc, \ell, \Gamma, f, G) ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = \\
     ~~~~~~~~~~~~~~~ [~ \$x \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = \\
     ~~~~~~~~~~~~~~~ \Con([~ \$x \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma, f, G) ~] \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x),
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  \todo{magic happens here}

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
  This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$. This means that the only state in $PG_{ij}$ connected to the start node ($\mathit{start}$) is a node for $l_{ij}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{ijk}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{ij} \}$ from the construction of the automata.

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m)  ~] ~] ~]\\
  \end{array} \]%
